Flowchart of Current Algorithm

### 2009-01-29 docs/flowchart/flowchart.tex
started a 'Future Considerations' section

@@

\MarginPar{Instead of calling Correct Base, if we set $\rho_0 = \overline\rho$, 
we don't even need $\nabla\cdot\etarho\er$.}
\item {\bf Correct Base}$[\rho_0^{\inp}, (\nabla\cdot\etarho\er)^{\inp}] \rightarrow [\rho_0^{\outp}]$\\
is the process by which we adjust the base state density to account for
large-scale mixing, through $\etarho$.  For both plane-parallel and spherical
we use
\begin{equation}
\rho_{0,j}^{\outp} = \rho_{0,j}^{\inp} - \dt (\nabla\cdot\etarho\er)^{\inp}_j \enskip . 
\end{equation}

>>>>

%-----------------------------------------------------------------------------
% Future Considerations
%-----------------------------------------------------------------------------

\section{Future Considerations}

\item Replacing {\bf Correct Base} with $\rho_0 = {\rm{\bf Avg}}(\rho)$ in 
plane-parallel and $\rho_0 = \rho_0 - {\rm{\bf Avg}}(\rho_0 - \rho)$ in spherical.  
This eliminates the need for $\nabla\cdot\etarho$.

\item After {\bf React State}, setting $(\rho h)_0 = {\rm{\bf Avg}}(\rho h)$ in 
plane-parallel and $(\rho h)_0 = (\rho h)_0 - {\rm{\bf Avg}}[(\rho h)_0 - (\rho h)]$ 
in spherical by making {\tt full\_rhoh0\_evolution = FALSE} by default.  This means
that {\bf Correct Base} no longer has to exist, and the intermediate states, 
$(\rho h)_0^{(1)}$ and $(\rho h)_0^{(2)}$, no longer have to exist.  
{\bf Advect Base Enthalpy} advances $(\rho h)_0^n \rightarrow (\rho h)_0^{n+1}$ directly.

\item Eliminating {\bf Advect Base Pressure} entirely, and instead enforcing HSE 
directly after {\bf Correct Base}.  {\bf Correct Base} should occur directly after 
creating $\etarho$, there is no need to delay the call as is currently being done.

@@

\item {\bf Correct Base}$[\rho_0^{\inp}, (\nabla\cdot\etarho\er)^{\inp}] \rightarrow [\rho_0^{\outp}]$\\
is the process by which we adjust the base state density to account for
large-scale mixing, through $\etarho$.  For both plane-parallel and spherical
we use
\begin{equation}
\rho_{0,j}^{\outp} = \rho_{0,j}^{\inp} - \dt (\nabla\cdot\etarho\er)^{\inp}_j \enskip . 
\end{equation}
